Analyzing the Impact of Social Attributes on Commit Integration Success

### 2017-03-28 Paper/MSRChallenge2017.tex
part of proof reading pass

\begin{abstract}
As the software development community makes it easier for everyone
to contribute to open source projects, the number of commits and pull requests 	
keep increasing. However, this exciting growth
renders it more difficult to only accept quality contributions.
Recent research has found 
that both technical and social factors predict
the success of project contributions on GitHub.  
We take this question a step further, focusing on predicting continuous
integration build success based on technical and
social factors involved in a commit.
Specifically, we investigated if social factors (such as being a
core member of the development team, having a large number of followers,
or contributing a large number of commits) improve predictions of build
success.  We found that social factors cause a noticeable increase
in predictive power (12\%), core team members are more likely to pass the build
tests (10\%), and users with 1000 or more followers are more likely to
pass the build tests (10\%).
\end{abstract}

@@

\section{Introduction}
For managers of an open source project, it is important to ensure that the
project consists of high quality contributions.  As social coding sites attract
more users and projects become more popular, they receive ever more
community contributions.  As the number of contributions to a project increase,
the project must dedicate more time to vetting these contributions. 
%
Over the years, the open source
community has developed various techniques to vet project contributions, such as pull
requests which must be approved by a core team member~\cite{gousios14}. 
This can become a bottleneck, and thus it is beneficial to prioritize certain
contributions, ideally by predicted quality.

Ideally, the decision to include code in
a project is meritocratic, such that only the code is a factor
in the decision~\cite{Scacchi07}.
While one would think that only the complexity of the commit is important, past
studies have shown that the developer making the commit is also an important
indicator when investigating contribution quality~\cite{tsay14icse, tsay14fse}.
Thus, both technical factors, which describe the complexity of the commit, and
social factors, which describe the developer's experience, are important when
investigating contribution quality.

This previous work has focused on the predicted acceptance of \emph{pull requests}. 
By contrast,  we are interested in analyzing the quality 
of a contribution in the context of \emph{continuous integration}.  While pull request
quality is determined through manual inspection, continuous integration quality
is automatically determined through test cases, and thus approach the problem of
quality determination differently.
We investigate the factors related to continuous integration build success.
In this study, we analyze a large set of technical and social attributes 
and how these can be used to predict a contribution's quality, measured by the
success of build integration jobs.
We performed this analysis on a large corpus of open source projects
which incorporated continuous integration in their development practice. 
When a contribution to these projects passes integration tests, 
it suggests that the project developers
might have confidence in the changes. 
Thus, we use the commit's build integration status as a proxy for its quality.

@@

We find that social factors are an important aspect of build success,
do not fully predict whether a contribution will 
pass all build tests;
that core team members are more likely to achieve build success than non-core
members; and that developers with more followers are more likely to submit commits that pass the
continuous integration build.

@@

\vspace{1ex}
\noindent\textbf{Goal.}
The \emph{goal} of this study is to identify and understand the relationship 
between the social factors that describe the
developer's experience (stars, followers, etc.) and technical properties that
describe a commit's complexity
(files added, files modified, etc.)
when predicting the likelihood that a developer's commit
will pass the continuous integration build tests for the project.

@@

\vspace{1ex}
\noindent \emph{Do social attributes, gathered from developers' GitHub profiles, allow for
  more accurate predictions of the developer's build success than only technical
  attributes?}

@@

Note also that the Kappa statistic increases in both cases when
adding social data (100\% and 85\% respectively). The Kappa statistic accounts
for the accuracy of the model's predictive power. It is more
robust than \textit{correctly classified} instances alone, since it takes into account the
correctly guessed instances occurring by chance. The precision, recall and
F-measure are calculated over the successful and unsuccessful classes and then
averaged (standard procedure in Weka).  All these measures increase with social
data in the feature space, making the prediction more reliable. The mean absolute error
decreases in both cases, further subtantiating the importance of social factors
in predicting build success.

>>>>

\begin{abstract}
As the software development community makes it easier 
to contribute to open source projects, the number of commits and pull requests 	
keep increasing. However, this exciting growth
renders it more difficult to only accept quality contributions.
Recent research has found 
that both technical and social factors predict
the success of project contributions on GitHub.  
We take this question a step further, focusing on predicting continuous
integration build success based on technical and
social factors involved in a commit.
Specifically, we investigated if social factors (such as being a
core member of the development team, having a large number of followers,
or contributing a large number of commits) improve predictions of build
success.  We found that social factors cause a noticeable increase
in predictive power (12\%), core team members are more likely to pass the build
tests (10\%), and users with 1000 or more followers are more likely to
pass the build tests (10\%).
\end{abstract}

@@

\section{Introduction}
For managers of an open source project, it is important to ensure that the
project consists of high quality contributions.  As social coding sites attract
more users and projects become more popular, they receive ever more
community contributions.  As the number of project contributions increase,
the project must dedicate more time to vetting these contributions. 
%
Over the years, the open source
community has developed various techniques to vet project contributions, such as pull
requests that must be approved by a core team member~\cite{gousios14}. 
This can become a bottleneck, and thus it is beneficial to prioritize certain
contributions, ideally by predicted quality.

Ideally, the decision to include code in
a project is meritocratic, such that only the code is a factor
in the decision~\cite{Scacchi07}.
While one would think that only the complexity of the commit is important, past
studies have shown that the developer making the commit is also an important
indicator for contribution quality~\cite{tsay14icse, tsay14fse}.
Thus, both technical factors, which describe the commit's complexity, and
social factors, which describe the developer's experience, are important when
investigating contribution quality.

Previous work has focused on the predicted acceptance of open source \emph{pull
requests}~\cite{tsay14icse, tsay14fse} and \emph{continuous integration} builds
in a single project.
By contrast,  we are interested in analyzing contribution quality 
in \emph{continuous integration} across multiple open source projects.  While 
pull request
quality is determined through manual inspection, continuous integration quality
is automatically determined through test cases, and thus may lead to different
quality predictors. 
We investigate the factors related to continuous integration build success
across open source projects.
In this study, we analyze a large set of technical and social attributes 
and how these can be used to predict a contribution's quality, measured by the
success of build integration jobs.
We performed this analysis on a large corpus of open source projects
which incorporated continuous integration in their development practice. 
When a contribution to these projects passes integration tests, 
it suggests that the project developers
might have confidence in the changes. 
Thus, we use the commit's build integration status as a proxy for its quality.

@@

We find that social factors are an important predictor of build success,
but do not fully predict whether a contribution will 
pass all build tests;
that core team members are more likely to achieve build success than non-core
members; and that developers with more followers are more likely to submit 
commits that pass the
continuous integration build.

@@

\vspace{1ex}
\noindent\textbf{Goal.}
The \emph{goal} of this study is to understand the relationship 
between social factors that describe 
developer's experience (stars, followers, etc.) and technical properties that
describe a commit's complexity
(files added, files modified, etc.)
when predicting whether a developer's commit
will pass the continuous integration build tests for the project.

@@

\vspace{1ex}
\noindent \emph{Do social attributes
improve the predictions of a contribution's build success when compared to
predictions from only technical attributes?}

@@

Note also that the Kappa statistic increases in both cases when
adding social data (100\% and 85\% respectively). The Kappa statistic accounts
for the accuracy of the model's predictive power. It is more
robust than \textit{correctly classified} instances alone, since it takes into account the
correctly guessed instances occurring by chance. The precision, recall and
F-measure are calculated over the successful and unsuccessful classes and then
averaged (standard procedure in Weka).  All these measures increase with social
data in the feature space, making the prediction more reliable. The mean 
absolute error decreases in both cases, further substantiating the importance 
of social factors
in predicting build success.
